\vspace{-1cm} Model simplicity breeds contempt: using simple models to answer basic questions on species' distributions

### 2021-02-12 manuscript/manuscript.tex
fixing the problem... maybe
lambda removed

While the value of gaining a mechanistic understanding of species' distributions is unquestioned (ref), a lot can be learned from shedding light on basic properties of species' realized niches. Indeed, there is no general agreement the shape of species distributions. While many ecological textbooks (Begon et al., 1990, Giller, 1984, Krebs, 1994) assume this to be unimodal and symmetric, some have warned that empirical distributions can take many different forms \citep{austin2002spatial}.

@@

>>>>

While the value of gaining a mechanistic understanding of species' distributions is unquestioned (ref), a lot can be learned from shedding light on basic properties of species' realized niches. Indeed, there is no general agreement the shape of species distributions. While many ecological textbooks (Begon et al., 1990, Giller, 1984, Krebs, 1994) assume this to be unimodal and symmetric, some have warned that empirical distributions can take many different forms \citep{austin2002spatial}. XX showed that... Other work on... have also...

@@

EXPLAIN WHY KNOWING THIS BASIC INFORMATION IS IMPORTANT 
WHY DO YOU CARE
ABUNDANCE CENTER HYPOTHESIS IDEA
HOW STEEP THE EDGES ARE RAPIDLY EXPANDING
https://eco.confex.com/eco/2020/meetingapp.cgi/Paper/86915
https://advances.sciencemag.org/content/5/11/eaaz0414
https://onlinelibrary.wiley.com/doi/full/10.1111/j.1466-8238.2009.00451.x
